Hydra Battles in Coq

### 2020-10-29 doc/hydras.tex
corrections to the documentation (pdf)

\subsection{Active Links}
The  links which appear in this pdf  document lead are of three possible kinds of destination:
\begin{itemize}
\item Local links to the document itself,
\item External links, mainly to \coq's page,
\item Local links to pages generated by \texttt{coqdoc}. According to the current makefile,
  we assume that the page generated from a library \texttt{XXX/YYY.v} is stored as
the relative address \texttt{../src/html/hydras.XXX.YYY.html} (from the location of the pdf).
Thus,  active links towards our \coq{} modules may be incorrect if you got this \texttt{pdf} document otherwise than by compiling the distribution available in
\url{https://framagit.org/casteran/hydra-battles-in-coq}.

@@

\node (foot) at (2,0) {$\bullet$};
\node (N1) at (2,2) {$\bullet$};
\node (N2) at (2,4) {$\bullet$};
\node (N3) at (2,6) {$\bullet$};
\node (H0) at (0,2) {$\Smiley[2][vertfluo]$};
\node (H1) at (0,8) {$\Smiley[2][vertfluo]$};
\node (H2) at (4,8) {$\Smiley[2][vertfluo]$};
\node (H5) at (4,4) {$\Smiley[2][vertfluo]$};
\node (H4) at (6,0) {$\Xey[2][lightgray]$};
\draw (foot) -- (N1)[very thick] ;
\draw (N1) -- (N2);
\draw (N2) -- (N3) ;
\draw (N3) to [bend left= 10]  (H1) ;
\draw (N3) to [bend right= 16] (H2);
\draw (foot) to [bend left= 10]  (H0) ;
\draw (N1) to [bend right= 16] (H5);
\end{tikzpicture}

@@

\node (foot) at (2,0) {$\bullet$};
\node (N1) at (2,2) {$\bullet$};
\node (N2) at (2,4)  {{\color{lightred}$\bullet$}};
\node (N3) at (2,6) {{\color{lightred}$\bullet$}};
\node (H0) at (0,2) {$\Smiley[2][vertfluo]$};
\node (H1) at (0,8) {$\Sey[2][lightred]$};
\node (H2) at (5,0) {$\Xey[2][lightgray]$};
\node (H5) at (4,4) {$\Smiley[2][vertfluo]$};
\node (ex) at (5,8) {};
\draw (foot) -- (N1)[very thick] ;
\draw (N1) -- (N2);
\draw  (N2) -- (N3)[draw=lightred];
\draw (N3) to   [bend left= 10](H1) [draw=lightred];
\draw [dashed] (N3) to [bend left= 10](ex);
\draw (foot) to [bend left= 10]  (H0) ;
\draw (N1) to [bend right= 16] (H5);
\end{tikzpicture}
\caption{A second beheading}
\label{fig:Hy2}
\end{figure}

@@

\node (H0) at (0,2) {$\Smiley[2][vertfluo]$};
\node (H5) at (4,0) {$\Xey[2][lightgray]$};
\draw (foot) -- (N1)[very thick,draw=lightred] ;
\draw (N1) -- (N2)[draw=lightred];
\draw (N2) -- (N3)[draw=lightred];
\draw (N2) -- (N31)[draw=lightred];
\draw (N2) -- (N32)[draw=lightred];
\draw (N2) -- (N33)[draw=lightred];
\draw (N2) -- (N34)[draw=lightred];
\draw (N3) to   [bend left= 10](H1) [draw=lightred];
\draw (N31) to   [bend left= 10](H11) [draw=lightred];
\draw (N32) to   [bend left= 10](H12) [draw=lightred];
\draw (N33) to   [bend left= 10](H13) [draw=lightred];
\draw (N34) to   [bend left= 10](H14) [draw=lightred];
\draw (foot) to [bend left= 10]  (H0) ;
\draw [dashed] (N1) to  [bend left= 10](exN4);
\end{tikzpicture}
\caption{A third beheading (wounded part in red) \label{fig:Hy4}}
\end{figure}

@@

So, the next chapters will present ordinal numbers and ordinal notations, and we will
look for a variant complex enough for proving the termination of all battles, but not too complex if possible.

@@

\label{cnf-math-def}
\label{chap:proof-term}
\label{chap:T1}

>>>>

\subsection{Active Links}
The  links which appear in this pdf  document lead are of three possible kinds of destination:
\begin{itemize}
\item Local links to the document itself,
\item External links, mainly to \coq's page,
\item Local links to pages generated by \texttt{coqdoc}. According to the current makefile (through the commands \texttt{make html} and \texttt{make pdf}), 
  we assume that the page generated from a library \texttt{XXX/YYY.v} is stored as
the relative address \texttt{../src/html/hydras.XXX.YYY.html} (from the location of the pdf)
Thus,  active links towards our \coq{} modules may be incorrect if you got this \texttt{pdf} document otherwise than by compiling the distribution available in
\url{https://github.com/coq-community/hydra-battles}.

@@

\node (foot) at (2,0) {$\bullet$};
\node (N1) at (2,2) {$\bullet$};
\node (N2) at (2,4) {$\bullet$};
\node (N3) at (2,6) {$\bullet$};
\node (H0) at (0,2) {$\Smiley[2][vertfluo]$};
\node (H1) at (0,8) {$\Smiley[2][vertfluo]$};
\node (H2) at (4,8) {$\Smiley[2][vertfluo]$};
\node (H5) at (4,4) {$\Smiley[2][vertfluo]$};
%\node (H4) at (6,0) {$\Xey[2][lightgray]$};
\draw (foot) -- (N1)[very thick] ;
\draw (N1) -- (N2);
\draw (N2) -- (N3) ;
\draw (N3) to [bend left= 10]  (H1) ;
\draw (N3) to [bend right= 16] (H2);
\draw (foot) to [bend left= 10]  (H0) ;
\draw (N1) to [bend right= 16] (H5);
\end{tikzpicture}

@@

\node (foot) at (2,0) {$\bullet$};
\node (N1) at (2,2) {$\bullet$};
\node (N2) at (2,4)  {{\color{lightred}$\bullet$}};
\node (N3) at (2,6) {{\color{lightred}$\bullet$}};
\node (H0) at (0,2) {$\Smiley[2][vertfluo]$};
\node (H1) at (0,8) {$\Sey[2][lightred]$};
%\node (H2) at (5,0) {$\Xey[2][lightgray]$};
\node (H5) at (4,4) {$\Smiley[2][vertfluo]$};
\node (ex) at (5,8) {};
\draw (foot) -- (N1)[very thick] ;
\draw (N1) -- (N2);
\draw  (N2) -- (N3)[draw=lightred];
\draw (N3) to   [bend left= 10](H1) [draw=lightred];
\draw [dashed] (N3) to [bend left= 10](ex);
\draw (foot) to [bend left= 10]  (H0) ;
\draw (N1) to [bend right= 16] (H5);
\end{tikzpicture}
\caption{A second beheading}
\label{fig:Hy2}
\end{figure}

@@

\node (H0) at (0,2) {$\Smiley[2][vertfluo]$};
%\node (H5) at (4,0) {$\Xey[2][lightgray]$};
\draw (foot) -- (N1)[very thick,draw=lightred] ;
\draw (N1) -- (N2)[draw=lightred];
\draw (N2) -- (N3)[draw=lightred];
\draw (N2) -- (N31)[draw=lightred];
\draw (N2) -- (N32)[draw=lightred];
\draw (N2) -- (N33)[draw=lightred];
\draw (N2) -- (N34)[draw=lightred];
\draw (N3) to   [bend left= 10](H1) [draw=lightred];
\draw (N31) to   [bend left= 10](H11) [draw=lightred];
\draw (N32) to   [bend left= 10](H12) [draw=lightred];
\draw (N33) to   [bend left= 10](H13) [draw=lightred];
\draw (N34) to   [bend left= 10](H14) [draw=lightred];
\draw (foot) to [bend left= 10]  (H0) ;
\draw [dashed] (N1) to  [bend left= 10](exN4);
\end{tikzpicture}
\caption{A third beheading (wounded part in red) \label{fig:Hy4}}
\end{figure}

@@

The next chapter is dedicated to a generic implementation of ordinal notations, and chapter~\ref{chap:T1} to a proof of termination of all hydra battles with the help of an ordinal notation for the interval $[0,\epsilon_0)$.

@@

\label{cnf-math-def}
\label{chap:T1}
